Model Optimization

### 2015-03-03 Figure5/abxD01.optimizingModel.Rmd
Eliminate space from figure folder names

@@

The % variance explained was 90.95. Otu13, followed by 3 and 1 were the most obvious influences on the model.

I've also performed this same script to a file without the untreated titration groups. This yields 82.69% variance explained.  Otu3 is the most important OTU in this dataset, followed by 13, 1, 20, 42. In fact all the top OTUs are mostly porphyromonadaceae, a lachnospiraceae, and alistipes. It almost seems from this data like resistance is more about the loss of these protective bugs as opposed to growth of *C. difficile* promoting bacteria.

>>>>

Going along with this I did correlation calculations between the delay data and nextDayCFU:
```{r, eval=FALSE}

meta <- read.csv('~/Desktop/mothur/abxD01/rf/abxD01.final.an.unique_list.0.03.subsample.0.03.pick.shared.rf.delay.regression.logtrans.filter16mintot.noUntr.csv',header=T)
#meta<-meta[1:96] #change based on number of OTUs above .05%, then add 2 for first two cols
meta$nextDayCFU <- 10^(meta$nextDayCFU)
c<-1
otu <- c()
cor.spear <- c()
pval.spear <- c()
cor.ken <- c()
pval.ken <- c()
for(i in 3:length(meta)){
  otu[c] <- colnames(meta[i])
  cor.spear[c] <- cor.test(meta[,2],meta[,i], method="spearman")$estimate
  pval.spear[c] <- cor.test(meta[,2],meta[,i], method="spearman")$p.value
  cor.ken[c] <- cor.test(meta[,2],meta[,i], method="kendall")$estimate #good to see because kendall handles ties
  pval.ken[c] <- cor.test(meta[,2],meta[,i], method="kendall")$p.value #but only works if this is tao-b and not tao-a which im not sure about
  c <- c+1
}

pval.spear<-p.adjust(pval.spear, method='BH') #adjust for multiple comparisons
pval.ken<-p.adjust(pval.ken, method='BH') #adjust for multiple comparisons

results = NULL
results <- matrix(c(otu, cor.spear, pval.spear, cor.ken, pval.ken), ncol=5)
colnames(results) <- c('otu','corSpear','pvalSpear', "corKen", "pvalKen")
results <- results[order(results[,3]),]  #order by pvalue column=3
write.table(results[1:dim(results)[1],], file="~/Desktop/mothur/abxD01/correlation/abxD01.final.an.unique_list.0.03.subsample.filter16mintotal.shared.correl.delay.noUntr.results.txt", sep="\t", row.names=FALSE)

@@
